Virginia Election Project

### 2023-05-03 about.qmd
annother commit

This website showcases some of my works during my time studying at GW.

```{r}

```

>>>>

Hello! My name is Giovanna Romariz Lino. I am 22 years old and I am originally from Londrina, Brazil. I have just graduated from George Washington University with a Bachelor of Science degree in Business with a double concentration in International Business and Finance and a minor in Journalism and Mass Communications. During university, I have held leadership roles in the Brazilian Student Association, Alpha Kappa Psi Business Fraternity, the GW Socially Responsible Fund, among others. I have spent 4 years living in Washington D.C., and I have also studied abroad in Milan, Italy, at Bocconi University during Spring, 2022. During my life, I have also lived in Canada, and done summer exchanges in the United States while I was in high school. I speak fluent English, Portuguese, intermediate Spanish, and basic Italian. I am an only child and my parents still live in Brazil.

During my time at university, I have interned in more than four companies in Brazil focused on finance and marketing. I have also participated in consulting projects in Washington D.C. My main focuses of work following graduation are on consulting and finance. Now, I am moving to New York in July, 2023, and joining Alphasights as an Associate working under their Consulting department.

If you want to know more about my professional experience, you can read my [resume.](https://docs.google.com/document/d/1cv7g5l-lgJfpHSnO49QV12rrD57OgwzQ/edit?usp=sharing&ouid=116938803250525408172&rtpof=true&sd=true)

### 2023-05-03 index.qmd
annother commit

Hi, I'm Giovanna and I'm a student at the George Washington University. I like business and finance and enjoy keeping up with fashion and italian cuisine.

@@

B.S. Degree in International Business and Finance from the George Washington University

@@

Reporting and Writing

Business Valuation

Marketing strategy

>>>>

Hi, welcome to my webiste! I'm Giovanna and I'm a student at the George Washington University.

@@

B.S. Degree in Business with a double concentration in International Business and Finance and a minor in Journalism and Mass Communications from the George Washington University in Washington D.C.

@@

Financial analysis and valuation

Reporting and writing

Inbound and Outbound Marketing Strategy

## Interests

Business podscasts, italian cuisine and fashion.

### 2023-05-03 newsstory.qmd
annother commit

Article published in the George Magazine for the GW Fashion Business Association. The articles talks about the luxury brand Burberry and its strategies on dealing with sustainability and ESG metrics in a more connected world.

**Burberry: the brand's dilemma with sustainability**

The fashion industry is the second largest polluter in the world and consumers are becoming more aware of this. There has been a push to prioritize companies that acknowledge the value of sustainability, and hesitation to support those that fail to address it. Sustainability is a primary concern for consumers and in order for companies to continue to optimize their sales and remain relevant, their designers and managers must address the topic immediately.

When it comes to sustainability, companies have different opinions. On one hand, some argue that becoming sustainable is too costly and not worth the effort. While on the other hand, some brands view this extra cost as something that will be compensated by new clientele. However, it seems that the vast majority of Millenial, Gen X, Gen Z consumers believe that sustainability is a significant issue and that it should be addressed in the fashion industry.

With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive. For example, in the luxury fashion industry, fur has always been an important medium. In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry. For that reason, some designers are beginning to swap fur for something faux. In my opinion, this shift is beneficial and will have a positive impact on a luxury brand's reputation.\

One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry. The company proved to be unique in the high fashion market when Thomas created Gabardine, a 'breathable, weatherproof and hardwearing fabric revolutionising rainwear'. Also adding to the originality of the brand is Thomas Burberry's creation of the iconic pattern-based scarves, purses, and trench coats. In 2017, when the company's annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year. With the major repercussion of the brand's lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change. The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.\

As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future. The brand has made several promises to become more sustainable for 2022. For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy. In addition, Burberry has released a 'Responsibility Agenda' to set goals for increasing sustainability within the company. The agenda focuses on three areas: product, company, and communities. Each area is centered on achieving progress by making the brand's product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\

The 'Responsibility Agenda' goals abides with the Paris Climate Agreement and the UN's 17 Sustainable Development Goals. Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company's supply chain. The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and 'Bronze Class' in RobecoSAM's 2018 Sustainability Yearbook.\

Furthermore, Burberry established partnerships aimed at increasing sustainability. First, Burberry collaborated with Elvis & Kresse, a sustainable company devoted to rescuing raw materials and transforming it into luxury accessories, to make 120 tons of wasted leather fabric into selling products. Second, the brand has launched a capsule collection made from Econyl, sustainable nylon made from regenerated fishing nets, fabric scraps and industrial plastic, developing a way to combat plastic waste while creating a circular fashion filled with luxury products.

Burberry is one example of a company that suffered political turmoil due to its unsustainable approaches to fashion. Now, the brand is fixing the problem by collaborating with sustainable brands, becoming more transparent with its consumers and stakeholders, and setting goals to increase sustainability at the company. My hope is that Burberry becomes an example for other haute couture to follow.

>>>>

# Voter Suppression in Texas

*September, 2022*

The expression 'Fraudulent Election' has risen into prominence once again as former president Donald Trump has questioned the veracity of the results of the 2020 Presidential Election, when he lost to current Democratic President Joe Biden. Texas, a traditional Republican state governed by Greg Abbott, answering to Trump's claims, has passed a Senate Bill tightening state election laws in 2022, which was retaliated with claims of voter suppression in the state of Texas.

In light of Abbott's third special season in government, Trump has pressured the current Texas Governor to pursue an election audit in most of the state's counties, claiming voter fraud and irregularities in the 2020 elections. Eight and a half hours later, Abbott's administration pursued a forensic auditing process on four of the state's major counties - Collin, Dallas, Harris (Houston included), and Tarrant, showcasing the influence that Trump still has on the state's Republican party. However, the vote reassessment did not uncover any impropriety, and there is no evidence of fraud in the state during the election period.

In response to Abbott's actions, Trump wrote a letter claiming that Texans \"do not trust (Abbott's) election system, and they want (his) leadership on this issue, which is the number one thing they care about.\"

In September 2021, Abbott signed a senate bill (SB1), which bans 24 hour voting, drive-thru voting, and imposes difficulties on voting for mail-in-ballot, people with disabilities and marginalized groups. Those measures also protect partisan poll watchers and set limits to those who help other voters, with their commitment of swearing under oath.

"What makes this bill and similar ones Republicans are pushing across the country even more un-American is that Republicans are using the 'Big Lie' about the 2020 election as a pretext to support them. The reality is that these bills have nothing to do with election integrity or security, but rather are discriminatory measures making it harder for all people to vote. These bills will have a disproportionate impact on communities of color," stated Eric Holder, the US attorney general under former president Barack Obama.

Democratic candidate for Governor, Beto O'Rourke, has argued in Newsweek that "voter suppression is on purpose and by design, working exactly as Greg Abbott intended". He criticized Abbott over reports that election officials have sent back unapproved mail-in-ballot to voters due to identification problems. Mail-in-ballots affects voters over 65 years of age who cannot provide a correct driver's license or social security number, military veterans, and overseas voters.

Furthermore, The New York Times found that after the primaries held in the beginning of 2022, Harris county, the most populous county in Texas, held that "areas with large Black populations were 44 percent more likely to have ballots rejected than heavily white areas." Jen Ramos, the political expert for JOLT Action, a progressive club that works with Texan Latinos, told Newsweek that ballot rejections in El Paso, a city with 85% Latinos, was 15 percent during primaries in 2022. The implementation of SB1 has resulted in civil rights groups and democrats filing lawsuits against the new legislation claiming it as an attempt of voter suppression for marginalized communities.

\"Instead of working on issues that actually matter, like protecting school kids from Covid or fixing our failing electrical grid, Abbott is focused on rigging our elections and implementing extreme, right-wing policies,\" said O\'Rourke to The New York Times.

The Gubernatorial Election of Texas in 2022 will be held with no online voter registration on Election Day; stricter ID policies especially for Latinos, communities of color, and people with disabilities, who are less likely to have an acceptable form of identification on hand; no 24 hour election period accommodation; increased limitations for voter's assistants; and stricter criminal penalties.

Abbott's administration continues to claim that the bill facilitates instead of suppresses the voting process, but, with all these obstacles, it is worth questioning the real agenda behind the SB1.

### 2023-05-03 portfolio.qmd
3rd commit
annother commit

---
title: "Portfolio"
---

Hi there this is my portfolio page! Yay...

This is an example of one of my [works](https://www.linkedin.com) during my time at GW.

>>>>

---
title: "Portfolio"
author: "Giovanna Lino"
---

Welcome to my portfolio. Additional past works are included in this [page](https://www.linkedin.com/in/giovannarlino/), which takes you to my Linkedln. profile.

# **GWFBA**

Articles published in the *George Magazine* for the **GW Fashion Business Association**.

## **Burberry: the brand\'s dilemma with sustainability**

*December, 2020*

The fashion industry is the second largest polluter in the world and consumers are becoming more aware of this. There has been a push to prioritize companies that acknowledge the value of sustainability, and hesitation to support those that fail to address it. Sustainability is a primary concern for consumers and in order for companies to continue to optimize their sales and remain relevant, their designers and managers must address the topic immediately.

When it comes to sustainability, companies have different opinions. On one hand, some argue that becoming sustainable is too costly and not worth the effort. While on the other hand, some brands view this extra cost as something that will be compensated by new clientele. However, it seems that the vast majority of Millenial, Gen X, Gen Z consumers believe that sustainability is a significant issue and that it should be addressed in the fashion industry.

With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive. For example, in the luxury fashion industry, fur has always been an important medium. In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry. For that reason, some designers are beginning to swap fur for something faux. In my opinion, this shift is beneficial and will have a positive impact on a luxury brand\'s reputation.

One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry. The company proved to be unique in the high fashion market when Thomas created Gabardine, a \'breathable, weatherproof and hardwearing fabric revolutionising rainwear\'. Also adding to the originality of the brand is Thomas Burberry\'s creation of the iconic pattern-based scarves, purses, and trench coats. In 2017, when the company\'s annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year. With the major repercussion of the brand\'s lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change. The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.

As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future. The brand has made several promises to become more sustainable for 2022. For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy. In addition, Burberry has released a \'Responsibility Agenda\' to set goals for increasing sustainability within the company. The agenda focuses on three areas: product, company, and communities. Each area is centered on achieving progress by making the brand\'s product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.

The \'Responsibility Agenda\' goals abides with the Paris Climate Agreement and the UN\'s 17 Sustainable Development Goals. Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company\'s supply chain. The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the \'Textiles, Apparel & Luxury Goods\' sector by the DJSI 2018, and \'Bronze Class\' in RobecoSAM\'s 2018 Sustainability Yearbook.

Furthermore, Burberry established partnerships aimed at increasing sustainability. First, Burberry collaborated with Elvis & Kresse, a sustainable company devoted to rescuing raw materials and transforming it into luxury accessories, to make 120 tons of wasted leather fabric into selling products. Second, the brand has launched a capsule collection made from Econyl, sustainable nylon made from regenerated fishing nets, fabric scraps and industrial plastic, developing a way to combat plastic waste while creating a circular fashion filled with luxury products.

Burberry is one example of a company that suffered political turmoil due to its unsustainable approaches to fashion. Now, the brand is fixing the problem by collaborating with sustainable brands, becoming more transparent with its consumers and stakeholders, and setting goals to increase sustainability at the company. My hope is that Burberry becomes an example for other haute couture to follow.

## **Psychedelic Patterns**

*October, 2021*

\
   Fashion is always trying to reinvent itself. During the pandemic, various fashion trends were revived. One in particular was psychedelic patterns. Inspired by the 70s, this type of print was first popularized by counterculture teenagers in the midst of social and political turmoil. The 'LSD fabric' made of colorful lines refers to a 'hallucinogenic\'' pattern that became the inspiration for other psychedelic shapes, and made it possible for the pattern to be produced quickly and appear as a 'groovy' style in movies. These patterns are known for their bold colors, sinuous lines and natural shapes.

In 2021, with the use of social media, this style is back in action. Tie dye is one of the most popular psychedelic patterns that has been revived. According to the trend-forecasting company Heuritech, during this Winter season, tie dye trends are expected to increase more than 6% when compared to previous seasons.  High end brands, along with local boutiques, have embraced this sense of nostalgia and have created collections based on this style. Brands such as Tom Ford, Collina Strada, Lecavalier, and Raf Simons have embraced the tie dye and other psychedelic prints in their Spring/Summer 2021 collections.

Raf Simons used colorblocked and defined swirls. The collection was named 'Teenage Dreams' inspired by the 1979 film Hair, which resembles the feeling of uncertainty and change that people are living nowadays. The pandemic has had a major impact on the return of the psychedelic. Dennis Nothdruft, head of exhibitions in the Fashion & Textile Museum in London, said that there is a feeling  of civil unrest and change that correlates with the use of different prints. There is nothing more 'youth revolt' than what occurred in the 70s and the current moment we are facing. With the return of these prints, there is an evocation for community and participation, providing sensory experiences to the fashion community.

One fashion commentator said that during the pandemic, people got used to looking at social media all the time. For a brand to stand out, it requires a creative collection, and nifty patterns are a way to achieve that. Ideally, a user would stop scrolling and wonder more about the brand when coming across a stylish psychedelic pattern dress. Psychedelic patterns are here to bring back that sense of revolt and freedom that people need in 2021, a freedom that is colorful and bold.

## **Fashion reinvention - Rihanna vs. Savage X Fenty**

*October, 2020*

On September 30, 2020, Rihanna showed her newest Savage X Fenty collection to all fashion lovers. Known for having an open and liberal approach to the fashion industry, Rihanna delivered a fashion show filled with diversity and inclusion, with models who identified as men, women, non-binary, and celebrities models as Paris Hilton, Lizzo, Bella Hadid, Normani, Cara Delavigne, Shea Couleé, among many others.

Rihanna started to add to the diversity conversation in fashion when she launched Fenty in 2017, being the first woman of color to be added to the LVMH group. From then, she started to portray diversity and body acceptance in all of her collections and fashion shows, and the 2020 fashion show was no different.

During the pandemic, people started to question the meaning of traditional fashion, and how can the industry be more inclusive. Quarantine gave people a lot of time to think about this aspect, giving more freedom to reinvent the industry and history of fashion shows. Rihanna was one of the designers who invested in this topic and brought to the public a fashion show that empowered people\'s sexuality and encouraged all to take ownership and pride of their bodies when using lingeries.

By taking this inclusive approach, Rihanna impacts not only the fashion industry, but also millions of followers, fans, and consumers who can now envision themselves in all Savage X Fenty lingeries. They feel represented, and that is key for both sales success, and, most importantly, for the reinvention of the fashion industry. Furthermore, it is necessary to understand that the show is not simply a marketing strategy. Rihanna once stated, "I want to make stuff that I can see on the people that I know and they come in all different shapes, sizes, races, religions." It is a part of who she is, and her brand showcases that. Therefore, it is more than just an opportunity taken to increase sales by jumping on a trending moment of body acceptance. It actually is the core value of the brand and of the designer.

Another concept incorporated in this show was a virtual theatrical experience. If you watched it, you know that the show was filled with dancers and performances. This unique model enhanced the powerfulness of the show when portraying diversity of genders, races, body heights, and weights. It was a very creative approach in comparison to regular fashion shows, especially when it is important to keep consumers\' attention to the show now that it has a virtual format. The performance is available on Amazon prime. It is shocking how a year ago this was never considered a possibility, and now, it's the new norm.

In a world where Victoria Secrets\' scandal showed that there is still low tolerance when it comes to diversifying lingerie models in the runways, Rihanna questions this status quo with the release of her 2020 Savage X Fenty collection, and does that by capturing its public with an incredible virtual experience!

\

\

### 2023-05-03 virginiaelectionresults.qmd
annother commit

## Comparing gov vs. prez results

@@

@@

#load saved joined data file from previous script
joined_vacomparison <- readRDS(here("processed_data", "joined_vacomparison.rds"))

@@

@@

```{r}
#what is the average democratic percentage for both presidential and government election in Accomack County?

@@

1.  Create a map of the republican vote in all of the counties for both president and governor.

2.  Analyze the counties with the biggest democratic victory.

3.  Analyze the counties with the biggest republican victory.

4.  Was there a county in which Biden won for which the democratic governor didn't?

>>>>

## Comparing gov vs. president results

@@

First, I am loading the saved joined data file from the previous script in the code above.

@@

joined_vacomparison <- readRDS(here("processed_data", "joined_vacomparison.rds"))

@@

Now, I selected th `joined_vacomparison`\` data to be analyzed, using the head function.

@@

Now, I want to find out what is the average democratic percentage for both presidential and government election in Accomack County?

@@

1.  Analyze the counties with the biggest Democratic victory.

2.  Analyze the counties with the biggest Republican victory.

3.  Was there a county in which Biden won for which the Democratic governor didn't?
